\documentclass[11pt]{article}

% page dimensions
\usepackage[top=.3in, bottom=.35in, left=0.35in, right=.35in]{geometry}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{enumitem}

% margin notes
\usepackage{marginnote}
\reversemarginpar

% font
\usepackage[T1]{fontenc}
\usepackage[rm,light,sfdefault]{roboto}

% spacing adjustments
\setlength\parindent{0pt} % no automatic indent
\setlength{\tabcolsep}{0em} % table horizontal spacing
\setlist{nosep}
\setlist[itemize]{label=$\circ$}
\renewcommand{\baselinestretch}{1} % line spacing

% custom commands
% \newcommand{\rsection}[1]{\hspace{-0.3in}\rotatebox[origin=l]{90}{\marginnote{#1}}\vspace{-1em}} % section with title in margin
\newcommand{\rsection}[1]{\vspace{1.5em}\textcolor{gray}{\Large \robotoslab #1}\vspace{0.5em}}
\newcommand{\bd}[1]{\textbf{#1}}
\newcommand{\bt}[1]{\textit{\textbf{#1}}} % bold title
\newcommand{\gap}[0]{\vspace{0.3em}} % gap between items
\newcommand{\sgap}[0]{\vspace{0.2em}} % small gap between items
\newcommand{\dash}[0]{ $-$ } % styled dash
\newcommand{\tabsep}[0]{\, / \,} % table separator
\newcommand{\arr}[0]{ $\hspace{0.2em}\rightarrow\hspace{0.2em}$ } % arrow
\newcommand{\gray}[1]{\textcolor{gray}{#1}}
\newcommand{\e}[0]{> }
\newcommand{\E}[0]{$\triangleright$ }
\newcommand{\class}[2]{\e #1 // #2}

\begin{document}
\pagenumbering{gobble} % avoid page numbering

\begin{tabularx}{\textwidth}{Xr}
    \robotoslab
    \begin{tabular}[x]{@{}l@{}}
        {\Huge Joseph Leavitt} \sgap \\
       % {\Large \href{}{}}
    \end{tabular}
&   \footnotesize
    \begin{tabular}[x]{@{}r@{}}
        (772) 812-7473 \\
        JoeLeav1@gmail.com \\
        https://github.com/JoeLeavitt \\
    \end{tabular}
\end{tabularx}
\rule{7.8in}{0.05em}

%\gap

\rsection{Education}

\bt{University of Central Florida} \hfill \gray{2014 - 2018}

Bachelor of Science in Computer Science \hfill GP\hspace{-0.5px}A: 3.2/4.0

\rsection{Skills}

\textbf{Languages}: Python, Java, JavaScript, HTML, CSS

\textbf{Frameworks and Libraries}: Node.js, Socket.IO, Polymer.js, TensorFlow, TensorFlow Object Detection API, TFLearn, NumPy, OpenCV, fast.ai, PyTorch

\textbf{Tools}: AWS, Jupyer, Vim, Cron, Bash, Terminal, Linux, macOS, Windows, Git, IntelliJ IDEA, tmux, WinSCP

\textbf{Deep Learning and Machine Learning}: Object Detection, Object Classification, Gradient Descent, Logistic Regression 

\rsection{Work Experience}

\bt{Harris Corporation}\dash Software Engineer: Image Processing\hfill \gray{July 2018 - Present}

\begin{itemize}
\item[$\bullet$] Built \textbf{Python} tool to automate Maritime data extraction, saving 2 - 5 days of manual extraction per week.
\item[$\bullet$] Utilize in-house deep learning tools and \textbf{TensorFlow}'s Object Detection API to build models for detecting ships and types of ships in satellite imagery. (\textbf{Python} and \textbf{NumPy})
\item[$\bullet$] Spearheaded all 4 stages of the machine learning pipeline: data processing, feature engineering and selection, modeling, and optimization.
\item[$\bullet$] Implemented a blur detection scheme from a research paper released by Microsoft Research Asia using \textbf{Python}, \textbf{NumPy}, \textbf{OpenCV}, and \textbf{PyWavelets}.
\item[$\bullet$] Continuously researching and implementing deep learning techniques to improve the ship detection model by improving accuracy and handling overfitting. 
\end{itemize} 

\gap

\bt{SavvySuit}\dash Software Engineer Intern \hfill \gray{May 2016 - November 2016}

\begin{itemize}
\item[$\bullet$] Implemented a search and search filtering feature to check for conflicts of interest in a database of attorney clients using \textbf{JavaScript}, \textbf{Polymer}, and \textbf{Node.js}.
\end{itemize}

\gap

\bt{Lockheed Martin} \dash Software Developer Intern \hfill \gray{August 2015 - May 2016}

\begin{itemize}
\item[$\bullet$] Developed software in \textbf{C} and \textbf{C++} for a classified military missile program. Focused on bug fixes and code refactoring.
\end{itemize}

\rsection{Projects}

\bt{Knest}\dash Team of 4 \hfill \gray{September 2017 - May 2018}

\begin{itemize}
\item[$\bullet$] \textbf{Won 1st in Discipline (Computer Science)} at Florida's State-Wide Senior Design Showcase 2018.
\item[$\bullet$] Knest is a desktop application that uses deep learning and image processing techniques to detect birds in large sets photos and enhance them. (\textbf{Python}, \textbf{TFLearn}, \textbf{TensorFlow}'s Object Detection API, \textbf{NumPy}, and \textbf{OpenCV}) 
\end{itemize}

\gap

\bt{Collaboard}\dash Team of 2\hfill \gray{January 2016}

\begin{itemize}
\item[$\bullet$] \textbf{Won 1st place} overall at PolyHacks Hackathon.
\item[$\bullet$] Collaboard is a web application that consists of a interactive whiteboard and chat. (\textbf{JavaScript}, \textbf{Socket.IO}, and \textbf{Node.js} with \textbf{Express.js})
\end{itemize}

\gap

\bt{Class-ify}\dash Individual project \hfill \gray{November 2015}

\begin{itemize}
\item[$\bullet$] \textbf{Won the education award} at KnightHacks Hackathon.
\item[$\bullet$] Class-ify is a lightweight Chrome Extension that injects Rate My Professor ratings into the the UCF's class search page. (\textbf{JavaScript})
\end{itemize}

\rsection{Extracurricular}

\bt{Grace Hopper Conference}\dash Hopper \hfill \gray{October 4 - 6, 2017}

\begin{itemize}
\item[$\bullet$] Nine hours of volunteer service at the world largest conference for women in computing.
\end{itemize}

\end{document}
